---
title: "MATH 216: In Class Activity 02/21"
author: "Your Name Here"
output:
  html_document:
    code_folding: hide
---

# Instructions: 

- Answer the following questions. When you have finished, upload the `.html` file to Canvas. 

**return** or **calculate** means just print it out.
```{r}
#ie. 
sum(1:10)
```
**create** or **save** means save the dataframe for future use.
```{r}
#ie. 
x<-sum(1:10)
```

# Challenge: Use `dplyr` and `%>%`


```{r include=FALSE}
library(tidyverse)
gapminder <- read.csv("gapminder.csv")
```

1. Explore the dataframe. What are the names of the columns? What does each row represent? How many rows are there? 

```{r}
names(gapminder)
nrow(gapminder)
```


2. Create a dataframe called `Africa` that has information about all the countries in Africa over time, but not for other continents. How many rows does your dataframe have and why?

```{r}
Africa <- gapminder %>% 
  filter(continent=="Africa")

nrow(Africa)
```

3. Create a dataframe called `NorthAmerica` that has the values for `country`, `year`, and population for Canada, the United States, and Mexico but not any other countries. 

```{r}
NorthAmerica <- gapminder %>% 
  filter(country=="Canada"|country =="Mexico"|country=="United States") %>% 
  select(country, year, pop)
```

4. Return the average life expectancy per country. Which has the longest average life expectancy and which has the shortest average life expectancy?

```{r}
values <- gapminder %>% 
  group_by(country) %>% 
  summarize(mean.life.expectancy = mean(lifeExp))

values %>% 
  arrange(mean.life.expectancy) %>% 
  summarize(min.mean.life.expectancy = min(mean.life.expectancy),
            max.mean.life.expectancy = max(mean.life.expectancy),)
```

5. Return the count of the total population in each of the continents in 2002. 

```{r}
gapminder %>% 
  filter(year==2002) %>% 
  group_by(continent) %>% 
  summarize(sum.pop = sum(pop, na.rm=T))
```

6. Return the mean GDP per capita of all countries in Africa in the year 2002. 

```{r}
gapminder %>% 
  filter(continent == "Africa", year==2002) %>% 
  group_by(country) %>% 
  summarize(mean.gdp = mean(gdpPercap))
```

7. Create a new column in the dataset called `gdp_billion` which is equal to the GDP in billions, calculated as `gdpPercap*pop/10^9`. Make sure to save this new column into the `gapminder` data. 
```{r}
gapminder <- gapminder %>% 
  mutate(gdp_billion = gdpPercap*pop/10^9)
```

8. Try your best to create the data frame `gdp_pop_bycontinients_by_year` from the `gapminder` dataset using `dplyr`commands. 

```{r}
gdp_pop_bycontinents_byyear <- read.csv("gdp_pop_bycontinents_byyear.csv")
```

```{r}
gdp_pop_bycontinents_byyear <- gapminder %>%
    group_by(continent,year) %>%
    summarize(mean_gdpPercap = mean(gdpPercap),
              sd_gdpPercap = sd(gdpPercap),
              mean_pop = mean(pop),
              sd_pop = sd(pop),
              mean_gdp_billion = mean(gdp_billion),
              sd_gdp_billion = sd(gdp_billion))
```

9. Explore the data on your own. Present a dataframe that think is interesting. 

```{r}

```




