---
title: "MATH 216: In Class Activity 02/26"
author: "Your Name Here"
output:
  html_document
---

# Instructions: 

- Answer the following questions. When you have finished, upload the `.html` file to Canvas. 


# Challenge: Use `tidyr`

```{r include=FALSE}
library(tidyverse)
gapminder <- read.csv("gapminder.csv")
gapminder <- as_tibble(gapminder)
```


1. Use the space below to reproduce the following dataset. 

(a) `sample_long`
```{r}
##          country year lifeExp
## 1      Australia 1992  77.560
## 2      Australia 1997  78.830
## 3      Australia 2002  80.370
## 4      Australia 2007  81.235
## 5         Canada 1992  77.950
## 6         Canada 1997  78.610
## 7         Canada 2002  79.770
## 8         Canada 2007  80.653
## 9  United States 1992  76.090
## 10 United States 1997  76.810
## 11 United States 2002  77.310
## 12 United States 2007  78.242
```

```{r}

```

(b) `sample_wide`
```{r}
##   year Australia Canada United States
## 1 1992    77.560 77.950        76.090
## 2 1997    78.830 78.610        76.810
## 3 2002    80.370 79.770        77.310
## 4 2007    81.235 80.653        78.242
```

2. Take notice of the code below. What looks weird about it? How could you fix it? 

```{r}
gapminder %>%  
  spread(year, gdpPercap)
```

3. Consider the  `country`, `year`, `population` columns for all the European countries in the gapminder dataset. Print out version of the table where columns 1 and 2 are the European countries. Columns 3 - 14 should represent the population of the countries each each of the years of study (1952, 1957, 1962, etc). 

```{r}

```


4. The first chunk is going to create a new wide datset. 

```{r just_run_me}
gapminder_wide <- gapminder %>% 
  group_by(continent,year) %>% 
  summarise(total_pop=sum(pop, na.rm=T)) %>% 
  spread(year, total_pop)
```

Look at the code below which tries to convert the wide data to long data. It should be giving you error. Why?  How could you fix it? 

```{r}
gapminder_wide %>% 
  gather(years, total_pop, 2:13)
```
