---
title: 'MATH 216: Assignment 4'
author: "Your Name Here"
output: 
  html_document
---

```{r include=FALSE}
library(tidyverse)
library(maps)
```

#  Instructions

- submit the .html file to Canvas
- you are encouraged to work together and ask your peers questions. Each person should submit their own work. 
- You may share parts of your code to ask or answer questions on Slack. You should avoid sharing (copying and pasting) the entirety of your answers.
- make sure you include at least one acknowledgement 

### Loading the data

```{r}
## maps
library(maps)
world_map <- map_data("world")  #to map countries in the world
states_map <- map_data("state") #to map states in the US
counties_map <-map_data("county") #to map counties in the US

## rnaturalearth
library(rnaturalearth)
worldmap <- ne_countries(scale = 'medium', type = 'map_units',returnclass = 'sf')
```

## Question 1: Display a map of the State of Vermont. The map should display all the counties in Vermont. Make sure your plot is well labeled. (Optional: put a marker where Middlebury College is located.) 

```{r}

```


## Question 2: Use `rnaturalearth` and the dataset `worldmap` to create a map of Africa. Shade the countries by the variable `economy` (contained within the `worldmap` dataset). Make sure your plot is well labeled.

```{r}

```


## Question 3: The following should help you create a dataset `world_data` which contains information about many countries in the world. Create a map in an area of the world of your choice (ie. Africa, Caribbean, etc.) shading each of the countries using the variable `phones` which represents the number of phones per 1000 people. Make sure your plot is well labeled.

```{r}
#read in and format dataset
data <- read.csv("https://ebmwhite.github.io/MATH0216/data/worlddata.csv")
data$Country <- as.character(trimws(data$Country))
data$phones <- as.numeric(data$phones)

#join map data with dataset
world_data <- left_join(world_map, data , by = "Country")
```


```{r}
#create a map! 

```



# Acknowledgements
Use this space to acknowledge anyone who has helped you with this lab. This could be a peer who helped you when you got stuck. This could be the peer tutor.  This could be your family or a friend for their support. **You must include at least one acknowledgement**. 