---
title: 'MATH 216: Assignment 5'
author: "Your Name Here"
output:
  pdf_document: default
  html_document: default
---

```{r include=FALSE}
library(tidyverse)
```

#  Instructions

- submit the .html file to Canvas
- you are encouraged to work together and ask your peers questions. Each person should submit their own work. 
- You may share parts of your code to ask or answer questions on Slack. You should avoid sharing (copying and pasting) the entirety of your answers.
- make sure you include at least one acknowledgement 
- The assignment is worth 15 points total. The specific number of points for each part is listed below. 

### Loading the data

You have decided to open an online store selling things to keep people busy and creative. 

```{r}
products <-read.csv("https://ebmwhite.github.io/MATH0216/assignments/products.csv")
orders <-read.csv("https://ebmwhite.github.io/MATH0216/assignments/orders.csv")
customers <-read.csv("https://ebmwhite.github.io/MATH0216/assignments/customers.csv")
```

A list of the products you sell is available in `products`. A list of your current orders is available in `orders`. A list of your customers is available in `customers`. 

Please click on each dataset to get familar with what each row represents and what columns are available. 

## Question 1: Print out a list of all the products you sell which cost under $10 (1 point)

```{r}
products %>% 
  filter(price <= 10)
```

## Question 2: How many puzzles have you sold? (1 point) 

```{r}
left_join(orders, products, by="product_id") %>% 
  filter(description == "puzzle") %>% 
  summarize(revenue = sum(quantity))
```

Some students may have used slightly different logic. As long as they get the answer 1, give them the point. 


## Question 3: Consider the order with `order_id=4`. What type of product did they order? (1 point)

Note: you can answer this by manually looking at the tables, or you can use the appropriate join function. 

```{r}
left_join(orders, products, by="product_id") %>% 
  filter(order_id == 4) %>% 
  select(description)
```

Some students may have used slightly different logic. As long as they get the answer "markers", give them the point. 


## Question 4: Consider the order with `order_id=7`. What is the email address associated with this order? (1 point)

Note: you can answer this by manually looking at the tables, or you can use the appropriate join function.

```{r}
left_join(orders, customers, by="customer_id") %>% 
  filter(order_id == 7) %>% 
  select(email)
```

Some students may have used slightly different logic. As long as they get the answer "jasmine007\@boxsquat.com", give them the point.

## Question 5 (6 points, 2 points for each part)

## (a) Return a dataframe which has all the columns and rows from `orders` but also contains an additional column with the `price` of the item listed in the `products` dataset. For example, if `product_id=3`, the column `price` should contain 8. 

```{r}
left_join(orders, products, by="product_id")  
  
```


## (b) In the `orders` dataset, add a new column called `total` which indicates the total cost of the order to the customer. You may want to use your answer from (a) to help you.

```{r}
left_join(orders, products, by="product_id")  %>% 
  mutate(total = price*quantity)
```

## (c) What is the total amount of revenue you have brought in so far? You may want to use your answer from (b) to help you. 

```{r}
left_join(orders, products, by="product_id")  %>% 
  mutate(total = price*quantity) %>% 
  summarize(revenue = sum(total))
```

## Question 6: List the names and addresses (including `address`, `city`, and `state`) of the people who placed orders on March 13, 2020. (2 points).  

```{r}
left_join(orders, customers, by="customer_id") %>%
  filter(time_stamp =="3/13/20") %>% 
  select(customer_name, address, City, State)
```

## Question 7: Find a dataset on Wikipedia that you think is interesting. Scrape the data from the web. Please include a link to the wikipedia pages and print out the first few rows of the dataset using the `head` command. 

You can choose any dataset you like. [https://en.wikipedia.org/wiki/Wikipedia:Featured_lists](https://en.wikipedia.org/wiki/Wikipedia:Featured_lists) might be a good place to start looking. 

Deduct points as you see appropriate... 
- 1 point deduction (2/3 marks) for not having the headers formatted appropriately
- 1 point deduction (2/3 marks) for not listing the source of their dataset somewhere
