---
title: 'MATH 216: Assignment 2'
author: "Your Name Here"
output: 
  html_document:
    code_folding: hide
---

```{r include=FALSE}
library(tidyverse)
```

#  Instructions

- please finish these questions by Wed, Feb 26. 
- submit the .html file to Canvas
- you are encouraged to work together and ask your peers questions. Each person should submit their own work. 
- You may share parts of your code to ask or answer questions on Slack. You should avoid sharing (copying and pasting) the entirety of your answers.
- make sure you include at least one acknowledgement 

# Loading the data

The following data is salaries at the University of North Carolina (UNC). Load it the data. 

```{r}
UNCdata <- read.csv("http://ryanthornburg.com/wp-content/uploads/2015/05/UNC_Salares_NandO_2015-05-06.csv")
```

Take a look at the data. Note what the column names are. Note what each row represents. Note that `fte` means full-time employee. 

# Problems

## Question 1

Return a data frame with columns: `name`, `dept`, `age`, `totalsal`

```{r}

```

## Question 2

Rename the `fte` column to `fulltime`. Make sure this change is saved (i.e. `data <-` ...).

```{r}

```

## Question 3

Return the mean salary in the Neurosurgery department?

```{r}

```


Return a data frame with employee’s in the Neurosurgery department making more than $500,000. 

```{r}

```

## Question 4

What is the total amount that full time Dermatology employees get paid?

```{r}

```


## Question 5

How many departments have at least 10 employees?

```{r}

```



## Question 6

Create a data frame called `radio_dept` whose rows are the employees from the Radiology department. 

- include only the following columns: `name`, `position`, `age`, `nonstsal`, `totalsal`. 
- order the employees by `salary`

```{r}

```

## Question 7

Create a data frame called `dept_summary`  whose rows are the departments and  whose columns are: department size, mean department salary, median department salary, and maximum salary (using `totalsal` for salary). 

```{r }

```


Order the departments by highest mean salary and print the 10 highest paid departments, on average. 

```{r }
#
```

Order the departments by highest median salary and print the 10 highest paid departments, on average. 

```{r }
#
```

Why do these lists differ? If you were asked for the top 10 best paid departments at UNC which summary would you choose and why?


## Question 8
Make a list of all the department names and sort this list alphabetically. What is the 42nd department in this list?

```{r }
#
```

# Acknowledgements
Use this space to acknowledge anyone who has helped you with this lab. This could be a peer who helped you when you got stuck. This could be the peer tutor.  This could be your family or a friend for their support. **You must include at least one acknowledgement**. 