---
title: 'MATH 216: Assignment 2'
author: "Your Name Here"
output: 
  html_document:
    toc: true
    toc_float: true
    theme: yeti
---

```{r include=FALSE}
library(tidyverse)
```

# Loading the data

The following data is salaries at the University of North Carolina (UNC). Load it the data and take a look through it. 

```{r}
data <- read.csv("http://ryanthornburg.com/wp-content/uploads/2015/05/UNC_Salares_NandO_2015-05-06.csv")
```

# Problems

## Question 1

Return a data frame with columns: `name`, `dept`, `age`, `totalsal`

```{r}

```

## Question 2

Rename the `fte` column to `fulltime`. Make sure this change is saved (i.e. data <- ...).

```{r}

```

## Question 3
What is the mean salary in the Neurosurgery department?

```{r}

```


Return a data frame with employee’s in the Neurosurgery department making more than $500,000. Why might these professors be so well paid?

```{r}

```

## Question 4

What is the total amount that full time Dermatology employees get paid?

```{r}

```


## Question 5

How many departments have at least 10 employees?

```{r}

```

## Question 6

Plot number of people hired by the CS dept per year vs. year

```{r}

```

# Acknowledgements
Use this space to acknowledge anyone who has helped you with this lab. This could be a peer who helped you when you got stuck. This could be the peer tutor.  This could be your family or a friend for their support. **You must include at least one acknowledgement**. 